Separating Use and Reuse to Improve Both

### 2017-05-18 FACS/paper.tex
local
.

Leveraging on \emph{traits}, in this work we aim to synthesizes
the main ideas of those very different language designs.
Our result is a nominally typed minimalistic language, natural to OO programmers.
By making our type system distinguish between code-use and code-reuse
we can separe inheritance and subtyping, while avoiding 
redundant abstract declarations (required in Delta-Trait and DeepFjig), while supporting self construction,
binary methods and recursive types.
Moreover, we provide a novel and elegant solution to uniformly
handle behavior and state within trait composition.

>>>>

Leveraging on \emph{traits}, in this work we aim to synthesizes
the main ideas of those very different language designs.
Our result is a nominally typed minimalist language, natural to OO programmers.
By making our type system distinguish between code-use and code-reuse
we can separate inheritance and subtyping, while avoiding 
redundant abstract declarations (required in Delta-Trait and DeepFjig), while supporting self construction,
binary methods and recursive types.
Moreover, we provide a novel and elegant solution to uniformly
handle behavior and state within trait composition.
